A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
shorter I think

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively\footnote{Compared to rewards from the original process
model.} small positive (negative) numeric quantity which captures the
utility the agent receives for correctly (incorrectly) rejecting an
assumption. A dual action can only be executed once, and corresponds
otherwise to a self-transition -- I.e., except in the applicability of
the dual, the process remains in the state from which a dual is
executed.
%%
Furthermore, if \switchAction\ is the action that switched the system
to a DT session, then an assumption $\assumptiveS{i}$ is only {\em
active} if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. We only include the duals of active assumptions in
DT sessions. For example, if the trace is:

@@

\noindent Usually dual rewards are sourced
from a motivational component of our robotic architecture. In this
paper, for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - \prob) / \prob$ where
$\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$
%%
Finally, execution of either a dual action $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session, which then continues from the underlying belief-state. If an
assumption was rejected, we prohibit that sequential session from
making it again.

>>>>

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively\footnote{Compared to rewards from the original process
model.} small positive (negative) numeric quantity which captures the
utility the agent receives for correctly (incorrectly) rejecting an
assumption. A dual action can only be executed once, and corresponds
otherwise to a self-transition -- I.e., except in the applicability of
the dual, the process remains in the state from which a dual is
executed.
%%
Furthermore, if \switchAction\ is the action that switched the system
to a DT session, then an assumption $\assumptiveS{i}$ is only {\em
active} if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. We only include the duals of active assumptions in
DT sessions. Continuing our simplified example, if the trace is:

@@

Execution of either a dual action $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session, which then continues from the underlying
belief-state. Turning to the detail of dual rewards, in our integrated
system these are sourced from a motivational subsystem. In this paper,
for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a small positive
constant, and have $\hat\$(x)= - \$(x)(1 - \prob) / \prob$ where
$\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$

\Omit{
%%
Finally, 
If an
assumption was rejected, we prohibit that sequential session from
making it again.
}
